### 2008-12-20 talk/ecoop2009/benchmarks.tex
fix another XXX

\anto{We should say somewhere that flexswitches are slow but benchmarks are so
  good because they are not involved in the inner loops}

@@

\commentout{
\cfbolz{I think we can kill this for space reasons}
\anto{If we decide to keep them, we must remember to explain the python-like
  syntax, as it is no longer in tlc.tex}

\begin{lstlisting}
def main(n):
    result = 1
    while n > 1:
        result = result * n
        n = n - 1
    return n
\end{lstlisting}
}

@@

\commentout{
\cfbolz{I think we can kill this for space reasons}
\begin{lstlisting}
def main(n):
    a = 0
    b = 1
    while n > 1:
        sum = a + b
        a = b
        b = sum
        n = n - 1
    return b
\end{lstlisting}
}

@@

>>>>

@@

@@

@@

As we saw in Section~\ref{sec:flexswitches-cli}, the implementation of
flexswitches on top of CLI is hard and inefficient.  However, our benchmarks
show that this inefficiency does not affect the overall performances of the
generated code.  This is because in most programs the vast majority of the
time is spent in the inner loop: the graphs are built in such a way that all
the blocks that are part of the inner loop reside in the same method, so that
all links inside are internal (and fast).
